% !TEX encoding = UTF-8
% !TEX TS-program = pdflatex
% !TEX spellcheck = it-IT
%% !TEX root = 
%% !BIB TS-program = biber

\documentclass[
	12pt,
	%German, % Uncomment for German
]{sty/report_style}
% \documentclass{article}
\usepackage[final, nonatbib]{sty/nips_2018}
\usepackage{sty/article_defaults}

\setminted[python]{linenos, breaklines, fontsize=\footnotesize}

%-------------------------------------------------------
%	ASSIGNMENT INFORMATION
%-------------------------------------------------------

\title{Practical Course on Computer Vision and Robotics} % Assignment title

\authorOne{Tommaso Bertola, 111111 ( $\leftarrow$ your student ID)} % Student name
\authorTwo{Marco Martinico, 111111} % Student name
\authorThree{Roberto Togni, 111111} % Student name

\date{15.02.2024 (t.b.a.)} % Due date

\institute{Georg-August-Universität Göttingen \\ Drittes Physikalisches Institut} % Institute or school name

\class{Practical Course on Computer Vision \& Robotics} % Course or class name

\professor{Sebastian Ruiz, Lennart Jahn} % Professor or teacher in charge of the assignment

%-------------------------------------------------------

\begin{document}

\maketitle

%-------------------------------------------------------
%	ASSIGNMENT CONTENT
%-------------------------------------------------------
\begin{problem}
    Write 3-6 pages (excluding appendix) for the following sections. Complete the table in \cref{appendix:time_schedule} and attach interesting pieces of code in \cref{appendix:code}.
\end{problem}

\section{Summary}

Give a short summary on the methods used and on the major discussion points.

\section{Method}

Write down your method for solving the task. What was your strategy? How did you construct the robot to perform the task?

For example, split into sections like this (or however you like):

\subsection{Computer Vision}

\subsection{Exploration}

\subsection{Mapping}

\subsection{Optimisation}

\section{Results}

Can you quantify any parts of your method? What is your accuracy in SLAM for example? How well does your path finding perform? etc...

\section{Discussion}

Discuss problems that you encountered with the robot and how you solved them. What worked well? What didn't work so well? What would you improve next time? 

\section{Teamwork}

Discuss how you divided the task. Mention what went well in the division of work and what could have gone better. Fill in the table in \cref{appendix:time_schedule}.

\clearpage
\appendix
\section{Time Schedule}\label{appendix:time_schedule}

Approximate time schedule and task distribution.

\begin{table}[h]
\begin{tabularx}{\linewidth}{@{}p{2cm}p{4cm}Xc>{\centering\arraybackslash}c@{}}
\toprule
Date                  & Group Member(s)        & Description of Work \\
\midrule
10/11/2022 & First name & Compiled the Operating system for the robot and wrote some code to test the motor functions. \\
\addlinespace[0.5em]
10/11/2022 & First name & Did something else. \\
\bottomrule
\end{tabularx}
\end{table}



\clearpage
\section{Code}\label{appendix:code}

Put interesting pieces of code here. Please also send all your code in a .zip file by email to \\ \href{mailto:sebastian.ruiz@uni-goettingen.de}{sebastian.ruiz@uni-goettingen.de}. 

\subsection*{Amazing Motor Controller}
%\inputminted{python}{example.py}

\subsection*{Path Finding Algorithm}
%\inputminted{python}{example2.py}

etc...

\end{document}
